\documentclass{eceasst}
% This is an empty ECEASST article that can be used as a template
% by authors.
% Just uncomment the appropriate frontmatter commands and provide
% the parameters.

% Required packages
% =================
% Your \usepackage commands go here.

% Volume frontmatter
% ==================
%\input{frontmatter}

% Volume frontmatter for AVoCS 2014
% =====================================
\volume{XXX}{2014} % Volume number and year
\volumetitle{% Title of the volume (optional)
Proceedings of the\\
14th International Workshop on\\
Automated Verification of Critical Systems
(AVoCS 2014)}
\volumeshort{% Short title of the volume (optional)
Proc.\ AVoCS 2014}
\guesteds{% Multiple guest editors
Marieke Huisman, Jaco van de Pol}
\title{Physical Type Tracking through Minimal Source-Code Annotation} % Title of the article
%\short{} % Short title of the article (optional)
\author{% Authors and references to addresses
Dave Donaghy\autref{1} and
Tom Crick\autref{2}}
\institute{% Institutes with labels
\autlabel{1} \email{dave.donaghy@hp.com}\\
HP Bristol, UK\par
\autlabel{2} \email{tcrick@cardiffmet.ac.uk}\\
Department of Computing\\
Cardiff Metropolitan University, UK}
\abstract{% Abstract of the article
One of many common artefacts of complex software systems that often
needs to be tracked through the entirety of the software system is the
underlying type to which numerical variables refer. Commonly-used
languages used in industry provide complex mechanisms through which
general objects are associated to a given type: for example,
the \begin{em}class\end{em} (and \begin{em}template\end{em})
mechanisms in Python (and C++) are extremely rich mechanisms for the
construction of types with almost entirely arbitrary associated
operation sets.

However, one often deals with software objects that ultimately
represent numerical entities corresponding to real-world measurements,
even through standardised SI units: metres per second, kilogram metres
per second-squared, etc.  In such situations, one can be left with
insufficient and ineffective type-checking: for example, the
C \begin{em}double\end{em} type will not prevent the erroneous
addition of values representing velocity (with SI units
\begin{em}metre per second\end{em}) to values representing mass (SI
unit \begin{em}kilogram\end{em}).

We present an addition to the C language, defined through the existing
\begin{tt}attribute\end{tt} mechanism, that allows automatic control
of physical types at compile-time; the only requirement is that
individual variables be identified at declaration time with
appropriate SI (or similar) units.

}
\keywords{Compilers, Plug-ins, Type-checking, Verification} % Keywords for the article

\begin{document}
\maketitle

% Main part of your article
% =========================
\section{Introduction}
Large (and indeed small) software systems typically track data, stored
in a variety of different types; in fact, ``bytes in, bytes out'' is a
fairly accurate description of a massive portion of the functionality
of large software systems. While this is clearly true, it is of course
an extraordinary over-simplification: the nature of the data we track
through software systems ultimately maps all of the data that
humankind has, can, or ever will, encompass.

It is not much of an understatement to say that tracking the types and
content of these data represents the whole job of software development.
Indeed, whole paradigms (for example, object-oriented development)
may be thought of as addressing this one significant issue. However,
such paradigms, while rich and functional, can also be cumbersome.

\section{Simple Techniques for Data Tracking}

In certain scenarios, the nature of the data we track may make it amenable
to simpler representation: from a mathematical point of view, while a C++
class representing a command-line instruction to be parsed and executed
\begin{em}is not\end{em} a mathematical object in any useful sense;
whereas a C++ object representing the distance from a geographical point
to another most assuredly is.

Nevertheless, it is common to either use the same complex,
powerful techniques to track these mathematical objects as to track
non-mathematical ones; or indeed not to effectively track them at
all. To contrast that idea, it might be possible to track these fundamentally
mathematical items in C-like languages in ways that allow minimal
additional effort at development time, and no maintenance effort at all.

For example, there is no meaningful way in which one can (or should)
add 10 metres to 20 kilograms; there \begin{em}is\end{em}, however, a
way in which we can multiply the two: the result has a value of 200,
and a unit of ``kilogram metre'' (one has to
understand \begin{em}slightly\end{em} more physics that the authors to
recall the precise physical meaning of a unit of ``kilogram metre'',
but one certainly exists).

\section{Implicit Type Operation and Restricted Types}

Imagine, then, that a variable declaration can be tagged with
a \begin{em}unit\end{em}; that two variables can be arbitrarily
multiplied; that two variables can be added if and only if their
underlying \begin{em}units\end{em} match exactly. With these abilities
in place, we could simply manipulate all physical types (kilograms,
metres, farads etc) as built-in numerical types, without resorting to
the complex \begin{em}class\end{em} mechanisms that we might otherwise
need.

We might call such a declaration a \begin{em}restricted type\end{em}:
being based on a built-in type (or indeed, any arbitrary type) it is
then further restricted by constraining the operations allowed on it:
no additional software is written to define the type, and the only
distinction between it and the type from which it is defined is this:
that with the new type, either the software compiled and behaves
identically, or it does not compile at all. While similar features
exist for certain programming paradigms (for example, functional
e.g. Haskell), there are significant opportunities for their
implementation in the languages commonly used for industrial software
development.


\section{Open Questions}

We can ask the following questions to frame future work in this area:

\begin{enumerate}

\item Which existing definitions of complex types (for example, C++
classes) can be replaced with restricted types?

\item By how much might software development effort be reduced using such techniques?

\item How much more effective might such techniques be at detecting software errors?

\end{enumerate}

% Acknowledgements for colleagues, referees, ...
% ==============================================
%\begin{acknowledge}
%\end{acknowledge}

% Bibliography with BibTeX
% ========================
%\bibliographystyle{eceasst}
%\bibliography{}

\end{document}
